POMDP comparisons across sigma_m, sigma_g

### 2017-10-07 appendix/appendix.Rmd
fix meta read

```{r}
log_dir <- "../pomdp_intro"
meta <- meta_from_log("pomdp_intro", log_dir)
alphas <- alphas_from_log(meta, log_dir)
```

@@

```{r}
sims %>%
  select(time, state, rep, method, sigma_m, sigma_g) %>%
  group_by(time, method, sigma_m, sigma_g) %>%
  summarise(mean = mean(state), sd = sd(state)) %>%
  ggplot(aes(time, mean, col=method, fill=method)) + 
  geom_line() + 
  geom_ribbon(aes(ymax = mean + sd, ymin = mean-sd), col = NA, alpha = 0.2) +
  facet_grid(sigma_m ~ sigma_g)
```

>>>>

```{r}
log_dir <- "../pomdp_intro"
meta <- meta_from_log("pomdp_intro", log_dir) %>% mutate(scenario=as.character(1:length(models)))
alphas <- alphas_from_log(meta, log_dir)
```

@@

```{r}
pomdp_sims %>%
  select(time, state, rep, method, sigma_m, sigma_g) %>%
  group_by(time, method, sigma_m, sigma_g) %>%
  summarise(mean = mean(state), sd = sd(state)) %>%
  ggplot(aes(time, mean, col=method, fill=method)) + 
  geom_line() + 
  geom_ribbon(aes(ymax = mean + sd, ymin = mean-sd), col = NA, alpha = 0.2) +
  facet_grid(sigma_m ~ sigma_g)
```
